\HeaderA{waved.example}{WaveD  examples}{waved.example}
\keyword{nonparametric}{waved.example}
\begin{Description}\relax
Generate data sets and figures
to illustrate the WaveD function.
\end{Description}
\begin{Usage}
\begin{verbatim}
waved.example(pr = TRUE, gr=TRUE)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{pr}] If pr=TRUE (default)
uses the same parameters as in the reference paper below. If pr=FALSE
user level parameter specifications. 
\item[\code{gr}] If gr=TRUE (default) text and graphical displays are provided.   
\end{ldescription}
\end{Arguments}
\begin{Value}
\begin{ldescription}
\item[\code{lidar.noisy}] Noisy blurred LIDAR signal (Gaussian noise)
\item[\code{lidar.noisyT}] Noisy blurred LIDAR signal (Student $t_2$ noise)
\item[\code{doppler.noisy}] Noisy blurred Doppler signal (Gaussian noise)
\item[\code{doppler.noisyT}] Noisy blurred Doppler signal (Student $t_2$ noise)
\item[\code{lidar.blur}] Blurred LIDAR signal
\item[\code{doppler.blur}] Blurred Doppler signal
\item[\code{t}] Rime vector scaled to  [0,1]
\item[\code{n}] Sample size
\item[\code{g}] Convolution kernel
\item[\code{lidar}] LIDAR signal
\item[\code{doppler}] Doppler signal.
\item[\code{seed}] Used in set.seed
\item[\code{sigma}] Noise standard deviation.
\item[\code{g.noisy}] Convolution kernel plus Gaussian noise.
\item[\code{g.noisyT}] Convolution kernel plus Student $t_2$ noise.
\item[\code{dip}] Degree of Ill-posedness.
\item[\code{k.scale}] Scale of the convolution kernel
\end{ldescription}
\end{Value}
\begin{Author}\relax
Marc Raimondo
\end{Author}
\begin{References}\relax
Raimondo, M. and Stewart, M. (2007),
"The WaveD Transform in R", Journal of Statistical Software.
\end{References}
\begin{SeeAlso}\relax
\code{\LinkA{WaveD}{WaveD}}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode} 
data=waved.example(TRUE,FALSE)
\end{ExampleCode}
\end{Examples}

